---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ppicalc: Calculator for Determining Poverty Likelihood Based on the Poverty Probability Index (PPI)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![CRAN](https://img.shields.io/cran/v/ppicalc.svg)](https://CRAN.R-project.org/package=ppicalc)
[![CRAN](https://img.shields.io/cran/l/ppicalc.svg)](https://github.com/ernestguevarra/ppicalc/blob/master/LICENSE.md)
[![CRAN](http://cranlogs.r-pkg.org/badges/ppicalc)](https://CRAN.R-project.org/package=ppicalc)
[![Travis-CI Build Status](https://travis-ci.org/ernestguevarra/ppicalc.svg?branch=master)](https://travis-ci.org/ernestguevarra/ppicalc)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ernestguevarra/ppicalc?branch=master&svg=true)](https://ci.appveyor.com/project/ernestguevarra/ppicalc)
[![codecov](https://codecov.io/gh/ernestguevarra/ppicalc/branch/master/graph/badge.svg)](https://codecov.io/gh/ernestguevarra/ppicalc)

Given `Poverty Probability Index (PPI)` scores based on the standard 10 questions on household’s characteristics and asset ownership, the likelihood that the household is living below the poverty line can be determined using this package. This package depends on country-specific lookup tables developed for the `PPI` available via the [`ppitables` package](https://github.com/validmeasures/ppitables).

## Installation

You can install `ppicalc` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("validmeasures/ppicalc")
```

## Usage

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
